working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-10 Manuscript_draft/Manuscript_draft.Rmd
seed set and fruit set information for 100% heterospecific pollen

Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the paiwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family Brassica oleracea and Eruca sativa we found very contrasting effects of foreign pollen where for the first one, all donors reduce seedt set significatively and for the second, just two species did out of nine. The treatments of 100% heterospecific pollen ... didn't seed except...

>>>>

Heterospecific pollen reduced seet set signifcatively with the 50-50% heterospecific pollen treatments for 65% of the pairwise interactions p<0.05. Across families we found a very similar effect but when species where look at species level they respond differently even within the same family, for instance for two species of the Brassicaceae family *Brassica oleracea* and *Eruca versicaria* we found very contrasting effects of foreign pollen where for the first one, all donors reduce seed set significatively and for the second, just two species did, out of nine. The treatments of 100% heterospecific pollen were all significantly different from the cross except one, *Sinapis alba* with pollen from another Brassicaceae, *Brassica oleracea*. Just few treatments of 100% pollen produced seeds... A summary of the results of hand cross pollination, self hand pollination, natural selfing and apomixis are presented in table 2.

### 2018-12-10 Manuscript_draft/Manuscript_draft.tex
seed set and fruit set information for 100% heterospecific pollen

Heterospecific pollen reduced seet set signifcatively with the 50-50\%
heterospecific pollen treatments for 65\% of the paiwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family Brassica oleracea and Eruca sativa we found very contrasting
effects of foreign pollen where for the first one, all donors reduce
seedt set significatively and for the second, just two species did out
of nine. The treatments of 100\% heterospecific pollen \ldots{} didn't
seed except\ldots{}

>>>>

Heterospecific pollen reduced seet set signifcatively with the 50-50\%
heterospecific pollen treatments for 65\% of the pairwise interactions
p\textless{}0.05. Across families we found a very similar effect but
when species where look at species level they respond differently even
within the same family, for instance for two species of the Brassicaceae
family \emph{Brassica oleracea} and \emph{Eruca versicaria} we found
very contrasting effects of foreign pollen where for the first one, all
donors reduce seed set significatively and for the second, just two
species did, out of nine. The treatments of 100\% heterospecific pollen
were all significantly different from the cross except one,
\emph{Sinapis alba} with pollen from another Brassicaceae,
\emph{Brassica oleracea}. Just few treatments of 100\% pollen produced
seeds\ldots{} A summary of the results of hand cross pollination, self
hand pollination, natural selfing and apomixis are presented in table 2.
